---
title: "Aides Drug"
author: "Kiara Butler!"
date: "09/21/23"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

A new preventative AIDS drug (triUmpsal) is under test in clinical trials. In this analysis, we will consider only the drug users and evaluate the effectiveness of this drug. We will use the dplyr package to filter the subpopulation of Drug Users.

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->


# Methods

In this section, describe the methods you will use for your analysis, such as variable analysis, graphical methods, and numerical methods. Discuss any data manipulations that may be needed, such as subsetting or binning procedures, and explain the graphical displays and inferential tools you plan to use. 

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->


```{r include=FALSE}

drug_users <- filter(triUmp, DrugUser == "yes")

drug_users

```

# Results


In the "Results" section, we present our findings in two sub-sections: "Descriptive Results" and "Inferential Results." In the "Descriptive Results," we utilize graphical representations, including bar charts illustrating both absolute counts and percentages, to visually depict the relationship between treatment (triUmpsal) and the likelihood of infection (infected) within the Drug Users population. Concurrently, we provide numerical insights through contingency tables, row percentages, and column percentages, offering a comprehensive quantitative analysis of infection rates across different treatment groups. Subsequently, within the "Inferential Results" subsection, we interpret the outcomes of our statistical tests, encompassing the chi-squared test, the chisqtestGC function, and Fisher's exact test. While the specific results, including p-values and test statistics, are not presented here, we emphasize the importance of these tests in determining whether a statistically significant association exists between treatment and infection, thereby shedding light on the effectiveness of the triUmpsal drug among Drug Users.


<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

Graphical Descriptive Results
Two bar charts are generated using the barchartGC function to visualize the relationship between the variables "infected" (likely indicating whether individuals contracted AIDS) and "treatment" (indicating whether they received the drug or not).
The first bar chart shows the absolute counts of infected and non-infected individuals for each treatment group.
The second bar chart displays the percentage of infected and non-infected individuals for each treatment group.
Numerical Descriptive Results
Contingency tables are created using xtabs, which provide counts of infected and non-infected individuals by treatment group.
Row percentages and column percentages are calculated using rowPerc and colPerc, respectively, to show the proportion of infected individuals within each treatment group and the proportion of individuals who received or did not receive treatment within the infected group. 

### Graphical Descriptive Results
 
 In this corrected version, I have fixed the formatting issues and added some explanatory sections. Make sure to fill in the "Methods" section with details about your analysis methods and any other relevant information. Additionally, you can expand the document with inferential results and conclusions as needed.
 
```{r}
barchartGC(~infected + treatment,data=drug_users)
barchartGC(~infected + treatment,data=drug_users, type="percent")

```


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=drug_users)
rowPerc(table1)
colPerc(table1)
```


We have calculated row percentages and column percentages for the contingency table representing the relationship between infection and treatment among drug users:



<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```  
 
 
 
 In this section, we will present any inferential results and conclusions based on our analysis of the data. Please provide details on the specific inferential tests or methods you used and the outcomes of these analyses.
 

  
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Discussion and Conclusion
 
the "triUmpsal" treatment and infection status among drug users in clinical trials, as indicated by variations in infection rates observed graphically and supported by numerical analysis. However, it's crucial to note that these findings do not establish causation but warrant further research, possibly through randomized controlled trials. Additionally, our study has limitations based on available data. If future research confirms the drug's effectiveness, it could have significant implications for AIDS prevention among drug users, though clinical decisions should rely on comprehensive studies. In summary, our analysis provides initial insights into "triUmpsal's" potential efficacy but underscores the need for rigorous research in public health interventions.


 
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
